Eco-evolutionary dynamics of finite populations from first principles

### 2023-04-16 MS_thesis.tex
Make bibliography more aesthetic
Minor rephrasing of acknowledgements
Add a new appendix for the lemma needed for alt rep of stoch integral terms

I would also like to thank Prof. Sutirth Dey, my expert for this project. Sutirth provided constructive comments during the mid-year evaluation that helped me re-evaluate my project and its goals. Sutirth's brilliant course on evolution at IISER and various fascinating conversations with him and other lab members during my time as an intern at the \href{https://sites.google.com/a/acads.iiserpune.ac.in/sdlab/pbl-iiser-p}{Population Biology Lab} have been instrumental in shaping my thoughts on evolution. I am also extremely grateful to Dr. Anand Krishnan for constantly supporting me and always being there when I needed advice --- Thank you for everything.

@@

%Import the Appendices
\chapter{From It\^{o} to Fokker-Planck}\label{App_SDE_FPE}
\input{ind_files/99_Appendix_A}
\chapter{Stochastic trait frequency dynamics using It\^{o}'s formula}\label{App_density_to_freq}
\input{ind_files/99_Appendix_B}
\chapter{A Price-like equation for the variance of a type-level quantity}\label{App_stoch_var_eqns}
\input{ind_files/99_Appendix_C}
\chapter{Some Examples}\label{App_examples}
\input{ind_files/99_Appendix_D_examples}

@@

%Ask the bibliography headers to say 'References' 
\fancyhead[CO]{\rule[-4ex]{0pt}{4ex}\footnotesize\itshape References}
%Add the phantomsection so that hyperref knows where to go
\cleardoublepage
\phantomsection
\vspace{-4.5cm}
\Huge\textbf{References}
%Add an entry in the table of contents
\addcontentsline{toc}{part}{References}
%Change the font for the bibliography
\renewcommand*{\bibfont}{\footnotesize}	
%Typeset the bibliography little differently using ragged2e
\begingroup
\RaggedRight
\vspace{2ex}
%Add the bibliography
\printbibliography[heading=none]
\endgroup
%And we're done :)
\end{document}

>>>>

I would also like to thank Prof. Sutirth Dey, my expert for this project. Sutirth provided constructive comments during the mid-year evaluation that helped me re-evaluate my project and its goals. Sutirth's brilliant course on evolution at IISER and various fascinating conversations with him and other lab members during my time as an intern at the \href{https://sites.google.com/a/acads.iiserpune.ac.in/sdlab/pbl-iiser-p}{Population Biology Lab} have been instrumental in shaping my thoughts on evolution. I am also extremely grateful to Dr. Anand Krishnan for constantly supporting me and always being there, both as a mentor and a friend, when I needed advice --- Thank you for everything.

@@

%Import the Appendices
\chapter{From It\^{o} to Fokker-Planck}\label{App_SDE_FPE}
\input{ind_files/99_Appendix_A}
\chapter{Stochastic trait frequency dynamics using It\^{o}'s formula}\label{App_density_to_freq}
\input{ind_files/99_Appendix_B}
\chapter{A Price-like equation for the variance of a type-level quantity}\label{App_stoch_var_eqns}
\input{ind_files/99_Appendix_C}
\chapter{Some Examples}\label{App_examples}
\input{ind_files/99_Appendix_D_examples}
\chapter{A more elegant representation of the stochastic integrals of Chapter \ref{chap_unification}}\label{App_alternative_representation}
\input{ind_files/99_Appendix_E_lemma}

@@

%Ask the bibliography headers to say 'References' 
\fancyhead[CO]{\rule[-4ex]{0pt}{4ex}\footnotesize\itshape References}
%Add the phantomsection so that hyperref knows where to go
\cleardoublepage
\phantomsection
\vspace*{1.3cm}
%Add a title for the bibliography
{\noindent\fontsize{48}{60}\selectfont \textbf{References}}
%Add an entry in the table of contents
\addcontentsline{toc}{part}{References}
%Change the font for the bibliography
\renewcommand*{\bibfont}{\footnotesize}	
%Typeset the bibliography little differently using ragged2e
\begingroup
\RaggedRight
\vspace{5ex}
%Add the bibliography
\printbibliography[heading=none]
\endgroup
%And we're done :)
\end{document}
